Exploring the Pareto front of multi-objective COVID-19 mitigation policies using reinforcement learning

### 2023-02-08 paper/main.tex
update arh vs ari setction

We now assess the difference in coverage sets when optimizing on $\mdprewardfn_\text{ARH}$ versus $\mdprewardfn_\text{ARI}$. Although at a different scale, our experiments show that infections and hospitalizations are correlated. This is confirmed in Figure~\ref{fig:pareto-front}: the coverage set \emph{in terms of hopsitalizations} learned by $\text{PCN}_\text{ARI}$ is only slightly worse than the one learned by $\text{PCN}_\text{ARH}$, even though $\text{PCN}_\text{ARI}$ optimized \emph{on the infection attack rate}. This is expected, as during the initial phase of the epidemic, limited immunity was present in the population (few natural immunity and no vaccines), which induces a tight coupling between infection and hospitalisation cases. Moreover, the opposite also holds: both coverage sets are similar in terms of \emph{infections}. However, there is one notable exception. A number of policies learned by $\text{PCN}_\text{ARH}$ start removing social restrictions before the epidemic is rooted out, resulting in a rise of hospitalizations at the end of the summer holidays. Since, following Abrams et al., this is when the simulation stops, the total number of hospitalizations remains low. The number of infections, however, starts growing before this rise in hospitalizations and, since its growth is exponential, ends up high. We note that $\text{PCN}_\text{ARH}$ also learns alternative policies for similar $[\mdprewardfn_\text{ARH}, \mdprewardfn_\text{SB}]$ that do not exhibit this behavior. This shows that, even though a policy might lead to a return that matches the preferences of the decision maker, its execution might still lead to undesired behavior. We argue that the use of such expert systems for decision making should be paired with careful interpretation.

>>>>

We now assess the difference in coverage sets when optimizing on $\mdprewardfn_\text{ARH}$ versus $\mdprewardfn_\text{ARI}$. Although these reward functions have a different scale (there are more infected persons than hospitalised ones), our experiments show that infections and hospitalizations are correlated. This is expected, as during the initial phase of the epidemic, limited immunity was present in the population (few natural immunity and no vaccines), which induces a tight coupling between infection and hospitalisation cases. This is confirmed in Table~\ref{tab:coverage-set}. In this table, we show the different performance metrics (hypervolume, $I_\varepsilon$, $I_{\varepsilon-mean}$) with respect to the objectives $[\mdprewardfn_\text{ARH}, \mdprewardfn_\text{SB}]$. However, the left-side of the table shows the experiments where these objectives are also used as optimization criterions, while the right-side shows the experiments using $[\mdprewardfn_\text{ARI}, \mdprewardfn_\text{SB}]$ as optimization criterions.

Even with the $\mdprewardfn_\text{ARI}$, the increased budget shows an increase in hypervolume in terms of hospitalisations. Moreover, those hypervolumes are close to the ones trained on $\mdprewardfn_\text{ARH}$, inidicating that their coverage sets are similar. However, regardless of the imposed budget, the hypervolumes are slightly worse. This is to be expected, since those experiments are not directly optimising on $\mdprewardfn_\text{ARH}$. We make similar conclusions for $I_\varepsilon$. For budgets 2, 3 and 5, the difference between the worst-performing policy for the $\mdprewardfn_\text{ARI}$ variant and the $\mdprewardfn_\text{ARH}$ is less than $0.01$, indicating less than $1\%$ difference in return values between the two variants when comparing their worst-performing policy. As an exception, we notice that PCN without budget restrictions results in better performance across every metric for the $\mdprewardfn_\text{ARI}$ variant. Still, due to the high standard deviation of the no-budget, $\mdprewardfn_\text{ARH}$ setting, we do not believe this difference is meaningfull. \todo{some kind of meaningfull conclusion}
